README

### 2017-04-11 src/README.Rmd
Use Packrat; Include MPMI in journal list

Twenty journals in the discipline of plant pathology were selected by the assignee as being the primary choice for most plant pathologists when publishing manuscripts.

@@

set.seed(1)
```
## Create list of journals

```{r journal_list}
journal_list <- tibble(
  seq(1:20),
  c("Australasian Plant Pathology",
    "Canadian Journal of Plant Pathology",
    "Crop Protection",
    "European Journal of Plant Pathology",
    "Forest Pathology",
    "Journal of General Plant Pathology",
    "Journal of Phytopathology",
    "Journal of Plant Pathology",
    "Journal of Plant Virology",
    "Molecular Plant Pathology",
    "Nematology",
    "Physiological and Molecular Plant Pathology",
    "Phytoparasitica",
    "Phytopathologia Mediterranea",
    "Phytopathology",
    "Plant Disease",
    "Plant Health Progress",
    "Plant Pathology",
    "Revista Mexicana de Fitopatología",
    "Tropical Plant Pathology"))

@@

```{r journal_sample}
journals <- tibble(sample(1:20, 200, replace = TRUE))
names(journals) <- "number"
journals <- left_join(journals, journal_list, "number")
```

@@

arrange(journals, assignee)

>>>>

Twenty one journals in the discipline of plant pathology were selected by the four authors as being the primary choice for most plant pathologists when publishing manuscripts.

@@

set.seed(1)

# For printing tibble in total
options(tibble.print_max = 21, tibble.print_min = 21)
```
## Create list of journals

```{r journal_list}
journal_list <- tibble(
  seq(1:21),
  c("Australasian Plant Pathology",
    "Canadian Journal of Plant Pathology",
    "Crop Protection",
    "European Journal of Plant Pathology",
    "Forest Pathology",
    "Journal of General Plant Pathology",
    "Journal of Phytopathology",
    "Journal of Plant Pathology",
    "Journal of Plant Virology",
    "Molecular Plant-Microbe Interactions",
    "Molecular Plant Pathology",
    "Nematology",
    "Physiological and Molecular Plant Pathology",
    "Phytoparasitica",
    "Phytopathologia Mediterranea",
    "Phytopathology",
    "Plant Disease",
    "Plant Health Progress",
    "Plant Pathology",
    "Revista Mexicana de Fitopatología",
    "Tropical Plant Pathology"))

@@

```{r journal_sample}
journals <- tibble(sample(1:21, 200, replace = TRUE))
names(journals) <- "number"
journals <- left_join(journals, journal_list, "number")
```

@@

arrange(journals, publication, year, start_page)
